Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Update Results

For social cohesion and count of all events, there was a consistent period 
of above-chance RR from the 7th-12th and 36th-47th window. DET was largely 
above chance from the 46th to the 61st window 
(Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of positive events, there was a downward trend in RR 
as the window moves with largely above-chance RR from the 1st-18th and 
32nd-45th windows. DET was at or above chance for the 8th-17th, 
32nd-34th and at the 60th window (Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of negative events, RR stayed above
or almost above chance from the 4th-7th and 43rd-47th windows. DET
was above or nearly above chance in the 1st and 2nd windows, with intermittent 
peaks in later windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and count of all events, there was a consistent period of
above- or nearly above-chance DET from the 7th-13th and 26th-47th 
windows. DET also showed above- or nearly above-chance values in windows 7 
through 17 and intermittent peaks between the 34th and 61st windows 
(Figure \@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion and count of 
positive events, there was a downward trend in RR as the window moved, with 
largely above-chance values in the first 20 windows and the 32nd-45th windows. 
DET stayed largely within chance, with the exception of windows 13 
through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion
and negative events, there was an extended period of time during which RR 
(32nd-47th windows) and DET (35th-39th windows) were above or nearly above 
chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)). These windows span from
May 3rd--14th, 2012.

>>>>

For social cohesion and count of all events, there was a consistent period 
of above-chance RR from the 7th--12th and 36th--47th window. In addition
to some one-week peaks at the beginning of the time period, DET was largely 
above chance from the 46th to the 61st window, with some exceptions 
(Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of positive events, we saw a downward trend in 
RR as the window advances throughout the sample. Interestingly, we see
largely above-chance RR until the 50th window, with some exceptions during
window periods 20-30. DET was at or above chance for the 7th--17th, 32nd-34th, 
and 60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of negative events, RR stayed above
or almost above chance from the 4th--7th and 43rd-47th windows. DET
was above or nearly above chance in the 1st and 2nd windows, with intermittent 
peaks in later windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and count of all events, there was a consistent period of
above- or nearly above-chance DET from the 7th--13th and 26th--47th 
windows. DET also showed above- or nearly above-chance values in windows 7 
through 17 and intermittent peaks between the 34th and 61st windows 
(Figure \@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion and count of 
positive events, there was a downward trend in RR as the window moved, with 
largely above-chance values in the first 20 windows and the 32nd--45th windows. 
DET stayed largely within chance, with the exception of windows 13 
through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion
and negative events, there was an extended period of time during which RR 
(32nd--47th windows) and DET (35th--39th windows) were above or nearly above 
chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)). These windows span from
May 3rd--14th, 2012.
